Data_Analysis_MS_ddm_exp1

### 2018-10-01 Results/preproc/MS_ddm_preproc.rmd
add questionnaire data

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_categ__rt_acc_long.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_noTask_l,'MS_categ__rt_acc_noTask_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

>>>>

# write files to an upper-level folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_categ__rt_acc_long.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_noTask_l,'MS_categ__rt_acc_noTask_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

```{r preproc questionnair,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# load the data
df.quest <- read.csv("exp7_survey_monkey_raw_c.csv",header = TRUE, sep = ',', stringsAsFactors=FALSE)

# calculate the reliability of each questionnair
# get the name and key for each scale
slfEsteemNames <- c( "slfEsteem_1", "slfEsteem_2", "slfEsteem_3", "slfEsteem_4", "slfEsteem_5",
                     "slfEsteem_6", "slfEsteem_7", "slfEsteem_8", "slfEsteem_9", "slfEsteem_10")
slfEsteemKeys  <- c(1,2,-3,4,-5,6,7,-8,-9,-10)        # for current dataset
slfEsteemKeys2 <- c( "slfEsteem_1", "slfEsteem_2", "-slfEsteem_3", "slfEsteem_4", "-slfEsteem_5",
                     "slfEsteem_6", "slfEsteem_7", "-slfEsteem_8", "-slfEsteem_9", "-slfEsteem_10")
slfEsteemAlpha <- psych::alpha(df.quest[,slfEsteemNames],keys = slfEsteemKeys) # alpha
print(slfEsteemAlpha$total[2])
slfEsteemOmega <- psych::omega(df.quest[,slfEsteemNames]) # omega
print(c(slfEsteemOmega$omega_h,slfEsteemOmega$omega.tot))

# calculate the score for the trait self-esteem
slfEsteemScore <- psych::scoreItems(slfEsteemKeys2,df.quest[,slfEsteemNames], totals = F, min = 1, max = 4)
df.quest$slfEsteem <- slfEsteemScore$scores

# calculate for moral identity
moralIdNames <- c("MoralId_1","MoralId_2","MoralId_3","MoralId_4","MoralId_5","MoralId_6",
                  "MoralId_7","MoralId_8","MoralId_9","MoralId_10","MoralId_11","MoralId_12",
                  "MoralId_13","MoralId_14","MoralId_15")
moralIdKeys <- c(1,2,3,4,-5,6,7,8,9,10,11,12,13,14,15)

moralIdAlpha <- psych::alpha(df.quest[,moralIdNames],keys = moralIdKeys) # alpha
print(moralIdAlpha$total[2])
moralIdOmega <- psych::omega(df.quest[,moralIdNames]) # omega
print(c(moralIdOmega$omega_h,moralIdOmega$omega.tot))

moralIdinNames <- c("MoralId_1","MoralId_2","MoralId_5","MoralId_8","MoralId_10",
                    "MoralId_11","MoralId_12", "MoralId_13","MoralId_14")
moralIdinKeys <- c(1,2,-3,4,5,6,7,8,9)
moralIdinKeys2 <- c("MoralId_1","MoralId_2","-MoralId_5","MoralId_8","MoralId_10",
                    "MoralId_11","MoralId_12", "MoralId_13","MoralId_14")
moralIdinAlpha <- psych::alpha(df.quest[,moralIdinNames],keys = moralIdinKeys) # alpha
print(moralIdinAlpha$total[2])
moralIdinOmega <- psych::omega(df.quest[,moralIdinNames]) # omega
print(c(moralIdinOmega$omega_h,moralIdinOmega$omega.tot))

# caculate the score for internal moral identity
moralIdinScore <- psych::scoreItems(moralIdinKeys2,df.quest[,moralIdinNames], totals = F, min = -2, max = 2)
df.quest$moralIdinScore <- moralIdinScore$scores

moralIdexNames <- c("MoralId_3","MoralId_4","MoralId_6",
                  "MoralId_7","MoralId_9","MoralId_15")
moralIdexKeys <- c(1,2,3,4,5,6)
moralIdexAlpha <- psych::alpha(df.quest[,moralIdexNames],keys = moralIdexKeys) # alpha
print(moralIdexAlpha$total[2])
moralIdexOmega <- psych::omega(df.quest[,moralIdexNames]) # omega
print(c(moralIdexOmega$omega_h,moralIdexOmega$omega.tot))

# calculate the score for external moral identity
moralIdexScore <- psych::scoreItems(moralIdexNames,df.quest[,moralIdexNames], totals = F, min = -2, max = 2)
df.quest$moralIdexScore <- moralIdexScore$scores

# find the intersection between behavioral data and questionnarie data.
tmp <- merge(df.v.sum_eff_all_w,df.quest[,c("subjID","slfEsteem","moralIdinScore","moralIdexScore")],by.x = "Subject",by.y = "subjID",all = TRUE)
tmp <- tmp[complete.cases(tmp),]

# write files to an upper-level folder
setwd(traDir)
write.csv(tmp,'MS_cross_taskeffect_wide_w_scale.csv',row.names = F)
setwd(curDir)
```
